master thesis

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Methods - rewrite OTL & GloBI

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Get data - Properties of real Data}
    For our research we need two types of data: a tree and information about the states. \\
    For the tree we decided to use Open Tree of Life (OTL). \\
    For the state information, we decided to use the Global biotic interaction database (GloBI).

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{OTL}
      For our project we looked for a large database for phylogenetic trees and also for a taxonomic 
        tree. Since we run our algorithm on the phylogenetic tree, and for the evaluation and other 
        properties the taxonomy provides us with much more information. \\
      OTL gives us both. A synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. 
        OTL also includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
      \todo{Das steht auf der Website nicht in dem Paper...} \\
      For phylogenetic data, there are at least five big data collections, namely: ITIS (Integrated 
        Taxonomic Information System) \cite{ITIS}, NCBI (National Center for Biotechnology Information) 
        \cite{NCBI1988}, WORMS (World Register of Marine Species) \cite{WoRMS2018}, GBIF (Global 
        Biodiversity Information Facility) \cite{GBIF}, OTT (OpenTreeOfLife-Taxonomy) 
        \cite{Hinchliff2015}. \\
      \todotext{Marius:} "Every dataset has it's own characteristics and downsides. ITIS is only a small 
        set of 100~\% confirmed and named species. GBIF is not composed with the help of phylogeny, the 
        same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small dataset of mostly 
        marine species. \\
      We choosed the taxonomy from OpenTreeOfLife because it's including most of the known taxonomies 
        and got synthesised by preffering taxonomies that match with available phylogenetic data. At the 
        same time the team from OTL preferred a maximum number of species \cite{Hinchliff2015}. This is 
        resulting in somekind of hybrid between taxonomy and phylogeny." \\

      We took a closer look at some of the features of the Synthesis tree. On the one hand the 
        distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this
        is not directly relevant to our study, there is a section in the appendix \ref{sec:otl analysis}.

@@

      This database consists of entries of the form: species A (source) interacts with B (target). \\
      We appointed some interactions\footnote{\hyperlink{
        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
        , where we know from the biological perspective that the species source or target has to be a 
        parasite or a free-living species. These are the following:
      \begin{itemize}
        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
          hasParasite, hostOf
        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
        \item parasite source: parasiteOf, pathogenOf
        \item parasite target: hasParasite, hasPathogen
      \end{itemize}
      We build two lists: parasites and free-livings, and add the source or targets of an interaction
        to these.

>>>>

  \todo{In den einzelnen Abschnitten Teile von dem großen Workflow verwenden?: \ref{fig:BigWorkflow}}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Description of data sets}
    For \colorbox{red}{our} research two types of data are required: a tree and information about the 
      states. \\
    For the tree \colorbox{red}{we} decided to use Open Tree of Life (OTL) \cite{Hinchliff2015}. \\
    For the state information, \colorbox{red}{we} decided to use the Global biotic interaction 
      database (GloBI) \cite{Poelen2014}.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{OTL}
      For \colorbox{red}{our} project a large database for phylogenetic trees and also for a taxonomic 
        tree is needed. Since an ancestral state reconstruction algorithm is applied to the phylogenetic 
        tree, and for the assessment and other properties the taxonomy provides much more information. \\
      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. OTL also 
        includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
      \todo{Das steht auf der Website nicht in dem Paper...} \\
      For phylogenetic data, there are at least five big data collections, namely:
      \begin{itemize}
        \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
        \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
        \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
        \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
        \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
      \end{itemize}
      \todo{In die discussion?:} \\
      ITIS is only a small set of 100~\% confirmed and named species. GBIF is not composed with the help 
        of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
        dataset of mostly marine species. \\
      Here the taxonomy from OTL is used because it is including most of the known taxonomies and is 
        synthesised by preffering taxonomies that match with available phylogenetic data. Furthermore 
        the team from OTL preferre a maximum number of species \cite{Hinchliff2015}. This is resulting 
        in somekind of hybrid between taxonomy and phylogeny. \anmerkungstext{Wie genau ist das ein 
        Hybrid? Genauer beschreiben, was Du damit meinst... (Thilo)} \\

      A closer look is being made to some of the features of the synthesis tree. On the one hand the 
        distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this 
        is not directly relevant to \colorbox{red}{our} study, there is a section in the appendix 
        \ref{sec:otl analysis}.

@@

      This database consists of entries of the form: species A (source) interacts with B (target). \\
      A number of interactions have been identified\footnote{\hyperlink{
        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
        ,including those that the species source or target has become a parasite or a free-living 
        species from the biological perspective. These are the following:
      \begin{itemize}
        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
          hasParasite, hostOf
        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
        \item parasite source: parasiteOf, pathogenOf
        \item parasite target: hasParasite, hasPathogen
      \end{itemize}
      Two lists are formed: parasites and free-livings, and the source or targets of an interaction
        are added to these.
